Vulnerability Analysis of Container Images in Neuroimaging

### 2020-04-06 paper.tex
added package removal script

Docker containers are managed by the Docker engine, which is a client-server application, and
is also known as Docker Daemon.

@@

\textit{Client:} It is a Command Line Interface (CLI) client which is used to interact with the \textit{Docker Daemon}.
convert english to punjabi
\end{comment}
%Docker runs a software, \textit{Docker daemon}, on the host machine.
Docker daemon runs as root and is remotely controlled through a
UNIX socket. It is responsible for launching and managing containers,
consequently, when a container runs, the container is spawned as a
child process of this root-owned daemon.

@@

Singularity is another tool for packing and running applications in containers. 
In our experiments, we used $2.5.2$ Singularity version. In contrast to Docker,
Singularity does not run containers as root. Consequently, users cannot escalate
privileges in Singularity containers making it suitable for HPC environments.

On the other hand, a Singularity image is a single immutable file and
does not contain layers.
Once a Singularity image is created, it cannot be changed, consequently,
it can be used for reproducing the results of scientific
experiments.

@@

BIDS apps~\cite{gorgolewski2017bids} is a framework designed to share and execute neuroimaging
analysis pipelines. It improves usability, accesibility, and reproducibility
of different applications through containerization.
At the time of this study, there were 27 BIDS apps available and all are using different Docker images.
Out of these 27 images, we used 26 images for our experiments because the QAP bids app was not available
on Docker hub.

So we have a total 38 Docker images from both BIDS Apps and Boutiques.
	Table~\ref{table1} displays the names of all the images that we took in our experiments.
%\begin{figure}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c},
%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
% late after line= \\,
%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{Existing number of Vulnerabilities}
%\end{figure}

@@

Anchore compares package versions, which are present inside the
image, with the vulnerability database to flag vulnerabilities.
To get a vulnerability feed of various OS distribution, Anchore refers to
different sources. For example, the Ubuntu launchpad database is used for Ubuntu.
In Ubuntu launchpad database, for a given CVE, there is an entry for all ubuntu releases.
Ubuntu releases are listed with the package name
in which vulnerability exists and are entitled a status
(\href{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
encoded in the following form:
\newline \\
\noindent <release>\_<source-package>: <status> (<version/notes>) \\
\newline\\
The status can be any one of the following:

@@

Ubuntu has ended support for some releases such as 14.04 LTS,
17.04, and 17.10, which means they have reached EOL. However, Ubuntu is providing optional extended support for Ubuntu 14.04.
To use this extended support, users have to buy ESM release for Ubuntu 14.04.
The images in our experiments have Ubuntu 14.04 LTS so scanners should refer
to LTS release only while collecting data from vulnerability databases. If scanners refer to ESM release for data it may result
in false positives and false negatives.
Also, if ubuntu releases with ended support are used in images, there are no chances of getting updates, hence
resulting in vulnerable images. Additionally, even if extended security is provided for some releases by Ubuntu, it is
not feasible to use it inside images because it is a paid service.

@@

@@

\bibliography{bibliography}

>>>>

Docker uses a client-server architecture, where client containers communicate to
the server Docker Daemon also known as Docker engine.
Docker Daemon is a long-running process that manages all Docker images, containers, storage volumes, and networks.

@@

\textit{Client:} It is a Command Line Interface (CLI) client which is used to interact with the \textit{Docker Daemon}.
convert english to punjabi
\end{comment}
%Docker runs a software, \textit{Docker daemon}, on the host machine.
It runs as root and is remotely controlled through a
UNIX socket. It is responsible for launching and managing containers,
consequently, when a container runs, the container is spawned as a
child process of this root-owned daemon.

@@

As Docker is not suitable for HPC systems therefore, Singularity came up with a new approach
of packing and running applications in containers. 
In contrast to Docker,
Singularity does not run containers as root. Consequently, users cannot escalate
privileges in Singularity containers making it suitable for HPC environments.

A Singularity image is a single immutable file and
does not contain layers.
Once a Singularity image is created, it cannot be changed, consequently,
it can be used for reproducing the results of scientific
experiments.

@@

\begin{comment}
\subsubsection{Brain Imaging Data Structure (BIDS) Apps}

BIDS apps~\cite{gorgolewski2017bids} is a framework designed to share and execute neuroimaging
analysis pipelines. It improves usability, accesibility, and reproducibility
of different applications through containerization.
At the time of this study, there were 27 BIDS apps available and all are using different Docker images.
Out of these 27 images, we used 26 images for our experiments because the QAP bids app was not available
on Docker hub.
\end{comment}
So we have a total 38 Docker images from both BIDS Apps and Boutiques.
	Table~\ref{table1} displays the names of all the images that we took in our experiments.
%\begin{figure}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c},
%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
% late after line= \\,
%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{Existing number of Vulnerabilities}
%\end{figure}

@@

Anchore compares package versions, which are present inside the
image, with the vulnerability database to flag vulnerabilities.
To get a vulnerability feed of various OS distribution, Anchore refers to
different sources. For example, the Ubuntu launchpad database is used for Ubuntu.

@@

Ubuntu has ended support for some releases such as 14.04 LTS,
17.04, and 17.10, which means they have reached EOL. However, Ubuntu is providing optional extended support for Ubuntu 14.04.
To use this extended support, users have to buy ESM release for Ubuntu 14.04.
The images in our experiments have Ubuntu 14.04 LTS so scanners should refer
to LTS release only while collecting data from vulnerability databases. If scanners refer to ESM release for data it may result
in false positives and false negatives.
Also, if ubuntu releases with ended support are used in images, there are no chances of getting updates, hence
resulting in vulnerable images.

Ubuntu maintains its vulnerability database in Ubuntu launchpad or Ubuntu CVE tracker. For a given CVE, there is an entry for all ubuntu releases.
Ubuntu releases are listed with the package name
in which vulnerability exists and are entitled a status
(\href{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
encoded in the following form:
\newline \\
\noindent <release>\_<source-package>: <status> (<version/notes>) \\
\newline\\
The status can be any one of the following:

@@

\subsection{Image size Reduction process}

If we want to reduce number of vulnerabilities without effecting the reproducibility of the image,
image size reduction process is a good choice. In this process we reduce the number of packages
installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
out which packages we need for the pipeline to fucntion properly. Here, we use Reprozip
\href{https://github.com/VIDA-NYU/reprozip}{https://github.com/VIDA-NYU/reprozip}. It is a tool that
is used to make applications reproducible~\cite{ChirigatiRSF16}. It traces operating system calls used by the
application while execution and then based on that it recognizes binaries, files, environment variables,
and library dependencies that will be used by the application for future reexecution. If the OS is
Debian or RPM based, Reprozip also
uses available package manager to acquire a list of distribution packages from where these files come from.
So, we got this list of packages from Reprozip that are needed for the application execution. 
After that, we expanded this list by adding important and required packages that are essential
for the system to function and finally figured out all the dependencies of these packages using debtree
(\href{http://manpages.ubuntu.com/manpages/xenial/man1/debtree.1.html}{http://manpages.ubuntu.com/manpages/xenial/man1/debtree.1.html}).
Ultimately, we kept these packages and removed remaining unnecessary packages. We used bash script

@@

Our last experiment shows deleting unnecessary packages from the image also helps to reduce
the number of vulnerabilities by significant number.
\bibliography{bibliography}
